---
title: "ODL's Lecture Note Database"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
  word_document: default
---


```{r setup}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
options(
  knitr.kable.NA = '',
  knitr.table.format = "latex"
  ) 
```

```{R Init}
library(dplyr)
library(kableExtra)
library(knitr)
load("repo.RData")
```
@.  The total file to upload are **`r total$Topics + total$Activity + total$"Self Check" + total$PPT` **. Each topics has to be uploaded separately by module. Each module which is in word format to be separated by topic and save to a pdf file. Total files and the learning type as in Table 1 - Files by Learning Type.

     **Table 1 - Files by Learning Type**

|Serial|Learning Type|Total
|------|-------------|----|
|1. |Lecture note by topic|`r total$Topics`
|2. |PPT Slides|`r total$PPT`
|3. |Microsoft Form (URL)|
|   |- Activities|`r total$Activity`
|   |- Self check|`r total$"Self Check"`
|4. |**Total**|**`r total$Topics + total$Activity + total$"Self Check" + total$PPT`**

@.   Whilst, there are `r nrow(module[is.na(module$Code),])` modules without the source file (.docx) as listed below:

     **Table 2 - Modules without the source file**

```{r missing module, echo=FALSE}
i <- c(0:6)
module %>% 
  filter(is.na(Code)) %>%
  mutate("Serial" = i + 1) %>% 
  select(Serial,Module,"Code"=Code_Doc,`YR-SM`) %>%
  arrange(`YR-SM`) %>%
  kable() %>% 
  kable_styling(full_width = FALSE)

```

@.  Modules without activity and/or self check:


     **Table 2(1) - Modules without Activity**

```{r activity is NA, echo=FALSE}
module_activity %>% 
  filter(is.na(Type)) %>% 
  inner_join(module) %>% 
  select(Module, Code, `YR-SM`) %>% 
  arrange(`YR-SM`) %>%
  kable() %>% 
  kable_styling(full_width = FALSE)

```

  **Table 2(1) - Modules without Self Check**

```{r self check is NA}
module_self_check %>% 
  filter(is.na(Type)) %>% 
  inner_join(module) %>% 
  select(Module, Code, `YR-SM`) %>% 
  arrange(`YR-SM`) %>%
  kable() %>% 
  kable_styling(full_width = FALSE)

```
     

@.  A script to automate the process to separate, convert and save each topics, the steps are:
    
    - Separate each topic from the source(.docx),
    - Verify the validity of the URL, figure and image source,
    - Annotation and clean the text, and
    - Convert each topic to markdown and save as pdf format.       

    **Table 3 - Summary of Module by Topics** (No Change)

```{r summary by module, eval=FALSE, include=FALSE}
module_topics %>% 
  bind_rows(module_activity) %>% 
  bind_rows(module_self_check) %>% 
  group_by(Module,Code,`YR-SM`) %>%
  select(Module, Topic, module_activity$Type) %>%
  summarise("Topics" = count(Topic), "Activity" = count(module_activity$Type)) %>%
  # count() %>%
  arrange(`YR-SM`) %>%
  # summarise("Topics" = sum(n)) %>% 
  kable() %>%
  kable_styling(full_width = FALSE) %>% 
  column_spec(1, bold = T, color = "red", width = "21em")

```

@.  The `r total$Topics + total$Activity + total$"Self Check" + total$PPT` files will be uploaded manually to the ODL database. List of files as Table 5 - Detail of Topics by Module. Average daily upload is **`r total$Module` / 7 days = `r round(total$Module/7)`** Module/day. The work start from **week 39** and expected to finish earliest in **week 44**. (see schedule below).

  **Table 4 - Schedule of Activity**

|Serial|Activity Week(Month)|W39|W40|W41|W42|W43|W44|W45|W46|Days
|------|-------------|---|---|---|---|---|---|---|---|-----
|1.|**File preparation**:|X||||||||7
||   - Write script to separate source file,
||   - Separate topics to markdown, and
||   - Each module is in it's own folder
|2.|**Edit and verify content in serial 1**.||X|X|X|X||||28
|| - edit content,
|| - verify URL,
|| - create activity/self check
|| - verify PPT slides
|3.|**Convert to pdf format**||X|||||||7
|4.|**HOD/Program Coordinator Approval**||||X|X||||14
||(1)  Documents will be sent in batches   
||       - Module 1 - 13
||       - Module 14 - `r nrow(module[!is.na(module$Code),])`
||       - Module (Reserved)
||(2) Confirmation by HOD/Program Coordinator|
|5.|**Upload materials to ODL database**||||||X|||7
||Module 1 - `r nrow(module[!is.na(module$Code),])`||||||X|
||PPT (`r nrow(module[!is.na(module$Code),])` files)|||||||X
||Activities and self-check (`r nrow(module[!is.na(module$Code),])` files)|||||||X
||**Total (Man-Days)**|||||||||`r 7+28+7+14+7`

@.  A weekly report to the HOD/Program Coordinator and a copy to Faculty's dean to update the upload progress. The format as in table 4(1) - Weekly Progress Report.

|Module,     |Code  ||Status(Topics, Activity & Self check, PPT) ||
|---------------|-----------|------------|-----------|-------|
|               |  | Preparatory|Work in Progress|Completed
|Communication and Counseling|BNBS 6124|15|||


  **Table 5 - Detail of Topics by Module** (No Change)

```{r module_topics, eval=FALSE, include=FALSE}
module %>% 
  select(Module,Code,"Year/Semester"=`YR-SM`) %>% 
  inner_join(module_topics) %>% 
  group_by(Module) %>% 
  kable(longtable =T,booktabs=TRUE) %>%
  kable_styling(latex_options =c("scale_down","repeat_header")) %>%
  column_spec(1, bold = T, color = "red", width = "15em") %>%
  column_spec(2:3, width = "7em") %>%
  column_spec(4, width = "19em") %>% 
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "top")

```

Prepared by: Colonel Hamdan bin Yaccob (R)

Date: `r format(Sys.Date(),"%d %b %y")`